### 2018-04-19 implementation.tex
fix layout

Unlike the other additions, explicitly designed for nondeterminism
detection, the {\tt P} query, {\tt forceP} wrapper, and {\tt --probability}, {\tt
  --samples}, and {\tt --replications} reducer options are general
tools for use with nondeterministic predicates in delta-debugging.  Of
course, nondeterminism and flakyness are the most common probabilistic
test properties we are aware of, but in theory these tools can be used
for other probabilistic debugging problems (e.g., if the property of
interest is that a value is above a certain threshold in 90\% of test
executions, these TSTL additions can be used to find a small test where this property
fails to hold).  In addition to the basic probabilistic reduction
issues discussed above, actual implementation of test reduction for
nondeterminism introduces some subtle issues.  By default, for
example, TSTL automatically removed non-enabled actions from tests
during reduction, because these are never actually executed.  However,
in timing based nondeterminism, such steps may be essential to
causing the nondeterminism to appear (we had to turn off this feature
in reducing the tests for the {\tt redis-py} example discussed below).

>>>>

Unlike the other additions, explicitly designed for nondeterminism
detection, the {\tt P} query, {\tt forceP} wrapper, and {\tt --probability}, {\tt
  --samples}, and {\tt --replications} reducer options are general
tools for use with nondeterministic predicates in delta-debugging.  Of
course, nondeterminism and flakyness are the most common probabilistic
test properties we are aware of, but in theory these tools can be used
for other probabilistic debugging problems (e.g., if the property of
interest is that a value is above a certain threshold in 90\% of test
executions, these TSTL additions can be used to find a small test where this property
fails to hold).  In addition to the basic probabilistic reduction
issues discussed above, actual implementation of test reduction for
nondeterminism introduces some subtle issues.  By default, for
example, TSTL automatically removed non-enabled actions from tests
during reduction, because these are never actually executed.  However,
in timing based nondeterminism, such steps may be essential to
causing the nondeterminism to appear (we had to turn off this feature
for the {\tt redis-py} example discussed below).
